---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The purpose of BetaBase is to provide functions for estimating and visualizing beta distributions, commonly used for Bayesian inference of probabilities. Functions are provided to:

* Determine the bounds of a credible interval containing a specified percent of the probability.
* Calculate the expectation of a beta distribution from its parameters.
* Determine the expected width of a confidence interval based on sample size.
* Estimate the parameters of a beta distribution from quantiles.
* Plot a beta distribution with optional interval shading and line indicating expected value.
* ggplot2 geoms for interval shading and line indicating expected value.

This introduction is intended to demonstrate the use of a few functions without going into detail about options. For more details see articles/vignettes for specific functions or function documentation.

```{r setup}
library(BetaBayes)
library(ggplot2)
```

Plotting a beta Beta(6, 4) distribution.

```{r}
plotdbeta(6, 4, expectation = TRUE, HDImass = 0.95)
```

Estimating beta parameters from quantiles.

```{r}
betaParamsFromQuantiles(q = c(0.1, 0.7))
```

Estimating width of confidence interval from sample size (and other parameters)

```{r}
df <- betaHDIwidthSim(genPriorMean = 0.1, genPriorN = 2)
ggplot(df, aes(n, HDIwidth)) +
  geom_path()
```
